Binocular combination in the autonomic nervous system

### 2025-02-06 manuscript.Rmd
Removed significance statement and modified figure 1 so that (d) now shows.

pdf(paste0(figdir,"methodsfigrods.pdf"), bg="transparent", height = 13, width = 12)

@@

text(5.5,14,'(d)',pos=4,cex=2)

@@

# Significance statement

Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas. We investigated the algorithmic properties of this binocular combination process for the first time. Using silent subsitution, we targeted different post-retinal pathways (light flux, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system. We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response. The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways. This elucidates the algorithm governing binocular combination in the autonomic nervous system.

>>>>

pdf(paste0(figdir,"methodsfigrods1.pdf"), bg="transparent", height = 13, width = 12)

@@

text(4.5,14,'(d)',pos=4,cex=2)

@@
